```{r}
title: "Stats Group Project"
output:
  pdf_document: default
  html_document: default
date: "2023-04-08"
editor_options:
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#import libraries
library(dplyr)
library(R.utils)
library(reshape)
library(tidyr)
library(psych)
library(ggplot2)
library(PerformanceAnalytics)
library(Hmisc)
library(chatgpt)
library(car)
#library(ggpmisc)
# library(ggrepel)
# library(sjPlot)
```
```{r Data, include=FALSE}
# read in data (remember to set working directory; this might take a few minutes becuase of how big the file is)
data <- read.csv('/Users/mohamadkhadra/Downloads/combined_clean_data-002.csv')
```
```{r Cleaning, include=FALSE}

#Stats Group Project 2023-04-08
# delete rows with missing data (1100 deleted)
data <- na.omit(data)
# convert to data frame
data <- data.frame(data)
# capitalize first letter in term column
data$term <- toupper(data$term)
# ensure all terms for each field in the data set are clean and showing as expected
unique(data$field)
unique(data$year)
unique(data$term)
# 2021 and 2022 have yet to be completely populated, which is evidenced by the below histogram.
# as such, we are going to set the range of this study to be from 1970 to 2020
# grouping data by year for plotting
years <- data %>% group_by(year) %>% dplyr::summarise(count = n())
# plotting the histogram
ggplot(years, aes(x = year, y = count)) +
geom_histogram(binwidth = 1, stat = "identity", width = 0.7, color =
"black") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
# changing units of labels
scale_y_continuous(labels = function(count) paste0(count/1000, "K")) +
ggtitle("Total Count per Year")
## Warning in geom_histogram(binwidth = 1, stat = "identity", width = 0.7, :
## Ignoring unknown parameters: `binwidth`, `bins`, and `pad`
# subset data to 1970-2020 (deleting incomplete 2021, 2022)
data <- subset(data, data$year<=2020)

# we then will ensure terms look acceptable as they'll be the other focus of our analysis
# grouping data by term for plotting
terms <- data %>%
group_by(term) %>%
dplyr::summarise(count = n())
# ordering the new data by count (ascending)
terms$term <- reorder(terms$term, terms$count)
# plot the bar chart
ggplot(terms, aes(x = term, y = count)) +
geom_bar(stat = "identity", width = 0.7, color = "black") +
# change x axis labels to be vertical
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
# changing units of labels
scale_y_continuous(labels = function(count) paste0(count/1000, "K")) +
ggtitle(("Terms by Count"))
# it does appear that we have some terms without few occurrences comparitively.
# these 5 terms are the least frequent
terms %>% arrange(count) %>% head(5)
# Despite the lower numbers, we will proceed with full set of terms while keeping this in mind.
# for the base of our analysis, we will will be looking at Term usage by Year.
# grouping data by term and year, and summarizing the count of terms by year.
byterm <- data %>% group_by(term, year) %>% dplyr::summarise(count = n())
## `summarise()` has grouped output by 'term'. You can override using the
## `.groups` argument.
# pivot df so that terms are column name
data_wide <- spread(byterm, term, count)
cor(data_wide[,-1], method="spearman", use="pairwise.complete.obs")
data_cor <- rcorr(as.matrix(data_wide[,-1]))
# Extract the correlation coefficients
data_cor$r
# Extract p-values
data_cor$P
# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values
flattenCorrMatrix <- function(cormat, pmat) {
ut <- upper.tri(cormat)
data.frame(
row = rownames(cormat)[row(cormat)[ut]],
column = rownames(cormat)[col(cormat)[ut]],
cor =(cormat)[ut],
p = pmat[ut]
)
}
flattenCorrMatrix(data_cor$r, data_cor$P)
## row column cor p
## 1 Abortion Activism 0.94555844
0.000000e+00
## 2 Abortion Civil rights 0.95920370
0.000000e+00
## 3 Activism Civil rights 0.92857534
0.000000e+00
## 4 Abortion Conservative 0.94982526
0.000000e+00
## 5 Activism Conservative 0.87257920
0.000000e+00
## 6 Civil rights Conservative 0.95195036
0.000000e+00
## 7 Abortion Discrimination 0.96385987
0.000000e+00
## 8 Activism Discrimination 0.92064883
0.000000e+00
## 9 Civil rights Discrimination 0.98192836
0.000000e+00
## 10 Conservative Discrimination 0.97117136
0.000000e+00

## 11 Abortion Diversity and inclusion 0.64876502
1.408160e-04
## 12 Activism Diversity and inclusion 0.77057947
1.008736e-06
## 13 Civil rights Diversity and inclusion 0.45053162
1.418181e-02
## 14 Conservative Diversity and inclusion 0.45878054
1.230648e-02
## 15 Discrimination Diversity and inclusion 0.56183951
1.515752e-03
## 16 Abortion Fatphobia 0.55777460
5.950784e-02
## 17 Activism Fatphobia 0.65852253
1.988513e-02
## 18 Civil rights Fatphobia 0.27591140 3.853664e-01
## 19 Conservative Fatphobia 0.38256153 2.196943e-01
## 20 Discrimination Fatphobia 0.53515756
7.298198e-02
## 21 Diversity and inclusion Fatphobia 0.92546260 1.597316e-05
## 22 Abortion Feminism 0.97801320
0.000000e+00
## 23 Activism Feminism 0.96836422
0.000000e+00
## 24 Civil rights Feminism 0.97235219
0.000000e+00
## 25 Conservative Feminism 0.94579226
0.000000e+00
## 26 Discrimination Feminism 0.97848452
0.000000e+00
## 27 Diversity and inclusion Feminism 0.68606121
3.985953e-05
## 28 Fatphobia Feminism 0.59953110 3.935682e-02
## 29 Abortion Human rights 0.95878160
0.000000e+00
## 30 Activism Human rights 0.94361490
0.000000e+00
## 31 Civil rights Human rights 0.98873092
0.000000e+00
## 32 Conservative Human rights 0.94703142
0.000000e+00
## 33 Discrimination Human rights 0.97880474
0.000000e+00
## 34 Diversity and inclusion Human rights 0.50293975

5.422456e-03
## 35 Fatphobia Human rights 0.37400788 2.310438e-01
## 36 Feminism Human rights 0.97110860
0.000000e+00
## 37 Abortion Immigration 0.97597613
0.000000e+00
## 38 Activism Immigration 0.97255809
0.000000e+00
## 39 Civil rights Immigration 0.97917517
0.000000e+00
## 40 Conservative Immigration 0.93674158
0.000000e+00
## 41 Discrimination Immigration 0.96773222
0.000000e+00
## 42 Diversity and inclusion Immigration 0.59107220
7.345891e-04
## 43 Fatphobia Immigration 0.42271126
1.709905e-01
## 44 Feminism Immigration 0.98299791
0.000000e+00
## 45 Human rights Immigration 0.98987087
0.000000e+00
## 46 Abortion Liberalism 0.95221570
0.000000e+00
## 47 Activism Liberalism 0.94211183
0.000000e+00
## 48 Civil rights Liberalism 0.96540789 0.000000e+00
## 49 Conservative Liberalism 0.91823039 0.000000e+00
## 50 Discrimination Liberalism 0.95233280
0.000000e+00
## 51 Diversity and inclusion Liberalism 0.52181188 3.693427e-03
## 52 Fatphobia Liberalism 0.29120224 3.584571e-01
## 53 Feminism Liberalism 0.96182006
0.000000e+00
## 54 Human rights Liberalism 0.95984196 0.000000e+00
## 55 Immigration Liberalism 0.96998418 0.000000e+00
## 56 Abortion Misogyny 0.89604793
0.000000e+00
## 57 Activism Misogyny 0.96238163
0.000000e+00
## 58 Civil rights Misogyny 0.84796590
1.036948e-13
## 59 Conservative Misogyny 0.81855018

3.687717e-12
## 60 Discrimination Misogyny 0.87257908
2.664535e-15
## 61 Diversity and inclusion Misogyny 0.90242890
2.238565e-11
## 62 Fatphobia Misogyny 0.88002125 1.595477e-04
## 63 Feminism Misogyny 0.93285230
0.000000e+00
## 64 Human rights Misogyny 0.85799382
2.575717e-14
## 65 Immigration Misogyny 0.89726366 0.000000e+00
## 66 Liberalism Misogyny 0.86553159 8.437695e-15
## 67 Abortion Nationalism 0.96941144
0.000000e+00
## 68 Activism Nationalism 0.95836009
0.000000e+00
## 69 Civil rights Nationalism 0.98923076
0.000000e+00
## 70 Conservative Nationalism 0.95062455
0.000000e+00
## 71 Discrimination Nationalism 0.98745219
0.000000e+00
## 72 Diversity and inclusion Nationalism 0.58758985
8.036761e-04
## 73 Fatphobia Nationalism 0.49523028
1.016160e-01
## 74 Feminism Nationalism 0.98880332
0.000000e+00
## 75 Human rights Nationalism 0.99266068
0.000000e+00
## 76 Immigration Nationalism 0.99057294
0.000000e+00
## 77 Liberalism Nationalism 0.96957606
0.000000e+00
## 78 Misogyny Nationalism 0.89440432
0.000000e+00
## 79 Abortion Patriarchy 0.96129176
0.000000e+00
## 80 Activism Patriarchy 0.98701364
0.000000e+00
## 81 Civil rights Patriarchy 0.93878823 0.000000e+00
## 82 Conservative Patriarchy 0.89996815 0.000000e+00
## 83 Discrimination Patriarchy 0.94390475

0.000000e+00
## 84 Diversity and inclusion Patriarchy 0.80002177 1.908001e-07
## 85 Fatphobia Patriarchy 0.76151702 4.005402e-03
## 86 Feminism Patriarchy 0.98201630
0.000000e+00
## 87 Human rights Patriarchy 0.94318655 0.000000e+00
## 88 Immigration Patriarchy 0.96773373 0.000000e+00
## 89 Liberalism Patriarchy 0.93677000 0.000000e+00
## 90 Misogyny Patriarchy 0.97218734
0.000000e+00
## 91 Nationalism Patriarchy 0.96418735 0.000000e+00
## 92 Abortion Patriotism 0.95228512
0.000000e+00
## 93 Activism Patriotism 0.94743832
0.000000e+00
## 94 Civil rights Patriotism 0.98672602 0.000000e+00
## 95 Conservative Patriotism 0.92818996
0.000000e+00
## 96 Discrimination Patriotism 0.97447735
0.000000e+00
## 97 Diversity and inclusion Patriotism 0.54952270 2.017184e-03
## 98 Fatphobia Patriotism 0.49621429 1.008322e-01
## 99 Feminism Patriotism 0.96716312
0.000000e+00
## 100 Human rights Patriotism 0.99077311 0.000000e+00
## 101 Immigration Patriotism 0.98164999 0.000000e+00
## 102 Liberalism Patriotism 0.95710959 0.000000e+00
## 103 Misogyny Patriotism 0.87289328
2.664535e-15
## 104 Nationalism Patriotism 0.98804861 0.000000e+00
## 105 Patriarchy Patriotism 0.95150903 0.000000e+00
## 106 Abortion Political 0.97993952
0.000000e+00
## 107 Activism Political 0.91841598
0.000000e+00
## 108 Civil rights Political 0.97919412 0.000000e+00
## 109 Conservative Political 0.97208015 0.000000e+00
## 110 Discrimination Political 0.99013502
0.000000e+00
## 111 Diversity and inclusion Political 0.55255249 1.882141e-03
## 112 Fatphobia Political 0.45468572 1.375212e-01
## 113 Feminism Political 0.98098079
0.000000e+00

## 114 Human rights Political 0.96809015 0.000000e+00
## 115 Immigration Political 0.96843186 0.000000e+00
## 116 Liberalism Political 0.95751766 0.000000e+00
## 117 Misogyny Political 0.87349994
2.442491e-15
## 118 Nationalism Political 0.97965735 0.000000e+00
## 119 Patriarchy Political 0.94569531 0.000000e+00
## 120 Patriotism Political 0.96028753 0.000000e+00
## 121 Abortion Politically correct 0.79716844
2.108255e-09
## 122 Activism Politically correct 0.69539483
1.262418e-06
## 123 Civil rights Politically correct 0.87801446
4.507505e-13
## 124 Conservative Politically correct 0.83593425
6.509548e-11
## 125 Discrimination Politically correct 0.88676524
1.272316e-13
## 126 Diversity and inclusion Politically correct 0.06909899
7.268001e-01
## 127 Fatphobia Politically correct -0.20435444 5.240670e-01
## 128 Feminism Politically correct 0.81747056
3.777445e-10
## 129 Human rights Politically correct 0.85077758
1.343015e-11
## 130 Immigration Politically correct 0.80563375
1.054774e-09
## 131 Liberalism Politically correct 0.84221625 3.404343e-11
## 132 Misogyny Politically correct 0.60872319
5.012298e-05
## 133 Nationalism Politically correct 0.85652536
6.958878e-12
## 134 Patriarchy Politically correct 0.72702475 2.350362e-07
## 135 Patriotism Politically correct 0.83700693 5.838774e-11
## 136 Political Politically correct 0.88587741 1.452172e-13
## 137 Abortion Prejudice 0.96984516
0.000000e+00
## 138 Activism Prejudice 0.98505515
0.000000e+00
## 139 Civil rights Prejudice 0.97591912 0.000000e+00
## 140 Conservative Prejudice 0.92278068 0.000000e+00
## 141 Discrimination Prejudice 0.96306030
0.000000e+00

## 142 Diversity and inclusion Prejudice 0.65440420 1.176317e-04
## 143 Fatphobia Prejudice 0.52212772 8.162588e-02
## 144 Feminism Prejudice 0.98599812
0.000000e+00
## 145 Human rights Prejudice 0.98219214
0.000000e+00
## 146 Immigration Prejudice 0.99467617 0.000000e+00
## 147 Liberalism Prejudice 0.96790153 0.000000e+00
## 148 Misogyny Prejudice 0.92564113
0.000000e+00
## 149 Nationalism Prejudice 0.98917971 0.000000e+00
## 150 Patriarchy Prejudice 0.98126247 0.000000e+00
## 151 Patriotism Prejudice 0.98079445 0.000000e+00
## 152 Political Prejudice 0.96168449 0.000000e+00
## 153 Politically correct Prejudice 0.78953657
3.830429e-09
## 154 Abortion Progressivism 0.95453544
0.000000e+00
## 155 Activism Progressivism 0.94719071
0.000000e+00
## 156 Civil rights Progressivism 0.97327115
0.000000e+00
## 157 Conservative Progressivism 0.91968365
0.000000e+00
## 158 Discrimination Progressivism 0.96186542
0.000000e+00
## 159 Diversity and inclusion Progressivism 0.56297652
1.475464e-03
## 160 Fatphobia Progressivism 0.32162084
3.080013e-01
## 161 Feminism Progressivism 0.97703048
0.000000e+00
## 162 Human rights Progressivism 0.96174986
0.000000e+00
## 163 Immigration Progressivism 0.97301693
0.000000e+00
## 164 Liberalism Progressivism 0.97332089 0.000000e+00
## 165 Misogyny Progressivism 0.88265429
4.440892e-16
## 166 Nationalism Progressivism 0.97990863
0.000000e+00
## 167 Patriarchy Progressivism 0.95313184 0.000000e+00
## 168 Patriotism Progressivism 0.95987341 0.000000e+00

## 169 Political Progressivism 0.96515620 0.000000e+00
## 170 Politically correct Progressivism 0.83656249
6.108447e-11
## 171 Prejudice Progressivism 0.97558262 0.000000e+00
## 172 Abortion Racism 0.92349005
0.000000e+00
## 173 Activism Racism 0.95756416
0.000000e+00
## 174 Civil rights Racism 0.88853388
0.000000e+00
## 175 Conservative Racism 0.86541508
2.220446e-16
## 176 Discrimination Racism 0.91375882
0.000000e+00
## 177 Diversity and inclusion Racism 0.88797887
1.322547e-10
## 178 Fatphobia Racism 0.91809579 2.526712e-05
## 179 Feminism Racism 0.94347346
0.000000e+00
## 180 Human rights Racism 0.90258956
0.000000e+00
## 181 Immigration Racism 0.92132613
0.000000e+00
## 182 Liberalism Racism 0.88748596
0.000000e+00
## 183 Misogyny Racism 0.97345091
0.000000e+00
## 184 Nationalism Racism 0.92787462
0.000000e+00
## 185 Patriarchy Racism 0.97570915
0.000000e+00
## 186 Patriotism Racism 0.91676706
0.000000e+00
## 187 Political Racism 0.90273321 0.000000e+00
## 188 Politically correct Racism 0.67948251
2.720260e-06
## 189 Prejudice Racism 0.94301235 0.000000e+00
## 190 Progressivism Racism 0.90084841
0.000000e+00
## 191 Abortion Sexism 0.92892661
0.000000e+00
## 192 Activism Sexism 0.98116027
0.000000e+00
38
## 193 Civil rights Sexism 0.88872500
0.000000e+00
## 194 Conservative Sexism 0.85575422
1.332268e-15
## 195 Discrimination Sexism 0.90523763
0.000000e+00
## 196 Diversity and inclusion Sexism 0.86558752
1.348925e-09
## 197 Fatphobia Sexism 0.80774074 1.483219e-03
## 198 Feminism Sexism 0.95478491
0.000000e+00
## 199 Human rights Sexism 0.90154314
0.000000e+00
## 200 Immigration Sexism 0.93700003
0.000000e+00
## 201 Liberalism Sexism 0.90267769
0.000000e+00
## 202 Misogyny Sexism 0.99091356
0.000000e+00
## 203 Nationalism Sexism 0.92844479
0.000000e+00
## 204 Patriarchy Sexism 0.98568669
0.000000e+00
## 205 Patriotism Sexism 0.91101328
0.000000e+00
## 206 Political Sexism 0.90446619 0.000000e+00
## 207 Politically correct Sexism 0.64446604
1.261844e-05
## 208 Prejudice Sexism 0.95566523 0.000000e+00
## 209 Progressivism Sexism 0.91500710
0.000000e+00
## 210 Racism Sexism 0.97439418
0.000000e+00
## 211 Abortion Terrorism 0.90682761
0.000000e+00
## 212 Activism Terrorism 0.90068548
0.000000e+00
## 213 Civil rights Terrorism 0.96011662
0.000000e+00
## 214 Conservative Terrorism 0.90906155 0.000000e+00
## 215 Discrimination Terrorism 0.96000773
0.000000e+00
## 216 Diversity and inclusion Terrorism 0.46393179 1.124401e-02

## 217 Fatphobia Terrorism 0.41491081 1.798659e-01
## 218 Feminism Terrorism 0.92506449
0.000000e+00
## 219 Human rights Terrorism 0.97115303 0.000000e+00
## 220 Immigration Terrorism 0.94466767 0.000000e+00
## 221 Liberalism Terrorism 0.92696426 0.000000e+00
## 222 Misogyny Terrorism 0.81950541
3.318013e-12
## 223 Nationalism Terrorism 0.95890613 0.000000e+00
## 224 Patriarchy Terrorism 0.89914021 0.000000e+00
## 225 Patriotism Terrorism 0.97458303 0.000000e+00
## 226 Political Terrorism 0.93269897
0.000000e+00
## 227 Politically correct Terrorism 0.82412939
2.051206e-10
## 228 Prejudice Terrorism 0.94229323 0.000000e+00
## 229 Progressivism Terrorism 0.91531368
0.000000e+00
## 230 Racism Terrorism 0.87185335 0.000000e+00
## 231 Sexism Terrorism 0.86207193 4.440892e-16
## 232 Abortion Transgender 0.78283502
2.103659e-10
## 233 Activism Transgender 0.90533105
0.000000e+00
## 234 Civil rights Transgender 0.69616429
1.097801e-07
## 235 Conservative Transgender 0.66059549
7.891103e-07
## 236 Discrimination Transgender 0.72811872
1.443048e-08
## 237 Diversity and inclusion Transgender 0.96405823
0.000000e+00
## 238 Fatphobia Transgender 0.87538235
1.913136e-04
## 239 Feminism Transgender 0.81726335
7.453815e-12
## 240 Human rights Transgender 0.72909626
1.350177e-08
## 241 Immigration Transgender 0.78934167
1.173814e-10
## 242 Liberalism Transgender 0.74179170
5.541201e-09
## 243 Misogyny Transgender 0.95915257

0.000000e+00
## 244 Nationalism Transgender 0.76858982
7.058865e-10
## 245 Patriarchy Transgender 0.89632931 0.000000e+00
## 246 Patriotism Transgender 0.75315391
2.387842e-09
## 247 Political Transgender 0.72091544
2.335752e-08
## 248 Politically correct Transgender 0.39483647
1.716536e-02
## 249 Prejudice Transgender 0.82663140
2.656764e-12
## 250 Progressivism Transgender 0.75360546
2.307132e-09
## 251 Racism Transgender 0.92098649
0.000000e+00
## 252 Sexism Transgender 0.94435190
0.000000e+00
## 253 Terrorism Transgender 0.69723582
1.029958e-07
## 254 Abortion Tribalism 0.93907201
0.000000e+00
## 255 Activism Tribalism 0.96786120
0.000000e+00
## 256 Civil rights Tribalism 0.91673401 0.000000e+00
## 257 Conservative Tribalism 0.88066354 0.000000e+00
## 258 Discrimination Tribalism 0.92827119
0.000000e+00
## 259 Diversity and inclusion Tribalism 0.72073069 1.035023e-05
## 260 Fatphobia Tribalism 0.59623644
4.073881e-02
## 261 Feminism Tribalism 0.96463675
0.000000e+00
## 262 Human rights Tribalism 0.93629177 0.000000e+00
## 263 Immigration Tribalism 0.95667314
0.000000e+00
## 264 Liberalism Tribalism 0.93282924 0.000000e+00
## 265 Misogyny Tribalism 0.92176665
0.000000e+00
## 266 Nationalism Tribalism 0.95443171 0.000000e+00
## 267 Patriarchy Tribalism 0.96024092 0.000000e+00
## 268 Patriotism Tribalism 0.93298624 0.000000e+00
## 269 Political Tribalism 0.92168248 0.000000e+00

## 270 Politically correct Tribalism 0.72443557
2.720280e-07
## 271 Prejudice Tribalism 0.95882857 0.000000e+00
## 272 Progressivism Tribalism 0.93297667
0.000000e+00
## 273 Racism Tribalism 0.92538987 0.000000e+00
## 274 Sexism Tribalism 0.95061449 0.000000e+00
## 275 Terrorism Tribalism 0.89275259 0.000000e+00
## 276 Transgender Tribalism 0.85892114
4.440892e-14
#Sourcetomodelatime-countexponentialcurve:https://stats.stackexchange.com/questions/261769/problems-with-plotting-exponential-curve-and-data-in-the-same-plot-when-values-a Referencecodeforloop:https://stackoverflow.com/questions/64500868/how-do-i-create-multiple-plots-by-looping-through-a-vertical-data-frame-in-r
#initializing temporary table to store pvalues
tmp_table = matrix(ncol=3)
# save one plot per term
# looping over each individual term
for (i in unique(byterm$term)) {
# filtering individual term into temporary vector
xterm <- byterm %>%filter(term==i)
# fitting model based on reference code
mod <- glm(count~year, data = xterm, family = "poisson")
# length.out measures length of x-axis which is 50 (1970-2020)
pred.df <- data.frame(year = seq(min(xterm$year), max(xterm$year),
length.out = 51))
# creating prediction model
pred <- predict(mod, newdata = pred.df, se.fit = TRUE)
# fitting exp count
pred.df$count <- exp(pred$fit)
# generating lowest count value for ribbon (CI)
pred.df$countmin <- exp(pred$fit - 2 * pred$se.fit)

# generating highest count value for ribbon (CI)
pred.df$countmax <- exp(pred$fit + 2 * pred$se.fit)
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
# Set up time variable to get year range for each term
time <- length(xterm$year)
range <- 1:time
# Define exponential growth function
exp_growth <- function(x, a, b) a * exp(b * x)
# Set growth rate
growth_rate <- 0.05 # 5% per year
# Get intercept value from predicted exponential curve
start_count <- pred.df$count[1]
articles <- exp_growth(range, start_count, growth_rate)
# data frame with year range and expected count
expected.df <- data.frame(year = xterm$year, count = articles)
# plotting model
colors <- c("Predicted" = "red", "Expected" = "blue")
plot <- ggplot(xterm,aes(x=year,y=count)) +
# setting x-limits for count
scale_x_continuous(limits=c(1970,2022),breaks=c(1970,
1975,1980,1985,1990,1995,
2000,2005,2010,2015,2020)) +
geom_point() +
geom_ribbon(data = pred.df, aes(ymin = countmin, ymax = countmax), alpha =
0.3) +
# plotting fitted curves
geom_line(data = pred.df, aes(y = count, color="Predicted")) +
geom_line(data = expected.df, aes(y = count, color="Expected")) +
annotate(geom = 'label', label = paste0("Predicted Growth Rate: ",
round(pred_rate, digits = 2), "%"),
x = -Inf, y = Inf, hjust = 0, vjust = 1) +
labs(x = "Year",

y = "Count",
color = "Legend") +
scale_color_manual(values = colors) +
ggtitle("Term:", i)
# showing plot
plot(plot)
#running one-sided poisson test for expected vs predicted growth rates
ptest <- poisson.test(
x = c(sum(as.integer(expected.df$count)), sum(as.integer(pred.df$count))),
T = c(length(expected.df$count), length(pred.df$count)),
alternative = 'less'
)
#saving and formatting pvalue
pvalue <- as.numeric(ptest[3])
results = c(i, pred_rate, pvalue)
#saving term and pvalue to table
tmp_table<-rbind(tmp_table,results)
}
#formatting stats_df
stats_df <- data.frame(tmp_table)
colnames(stats_df) <- c("Terms", "Predicted Growth Rate", "P Values")
stats_df <- stats_df[-1,]
rownames(stats_df) <- 1:nrow(stats_df)
stats_df$`P Values` <- signif(as.numeric(stats_df$`P Values`), 5)
stats_df$`Predicted Growth Rate` <- paste0(stats_df$`Predicted Growth Rate`,
"%")
stats_df
# Terrorism
terrorism <- subset(byterm, byterm$term == "Terrorism")
d1 = data.frame(subset(terrorism, terrorism$year <=1980))
d2 = data.frame(subset(terrorism, terrorism$year >=1980 & terrorism$year
<=1990))
d3 = data.frame(subset(terrorism, terrorism$year >=1990 & terrorism$year
<=2000))
d4 = data.frame(subset(terrorism, terrorism$year >=2000 & terrorism$year
<=2010))

d5 = data.frame(subset(terrorism, terrorism$year >=2010 & terrorism$year
<=2020))
yr_list = list(d1,d2,d3,d4,d5,terrorism)
yr_tmp = list()
for (i in 1:6){
dt = yr_list[[i]]
# fitting model based on reference code
mod <- glm(count~year, data = dt, family = "poisson")
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
yr_tmp[[i]] <- pred_rate
}
#Convert list to dataframe
yr_df <- data.frame(yr_tmp)
#Add correct column name per decade
names(yr_df) <-
c("1970-1980","1980-1990","1990-2000","2000-2010","2010-2020", "1970-2020")
#Round numbers to 2 digits and add %
yr_df <- round(yr_df, 2)
yr_df[] <- Map(paste, yr_df, "%")
yr_df
## 1970-1980 1980-1990 1990-2000 2000-2010 2010-2020 1970-2020
## 1 21.78 % 10.93 % 10.75 % 10.58 % 0.02 % 9.62 %
#to export to png
# library(gridExtra)
# png("yr_df.png", height = 50*nrow(yr_df), width = 200*ncol(yr_df))
# grid.table(yr_df)
# dev.off()
# Subset term
terrorism <- subset(byterm, byterm$term == 'Terrorism')
# fitting model based on reference code
mod <- glm(count~year, data = terrorism, family = "poisson")
# length.out measures length of x-axis which is 51 (1970-2020)
pred.df2 <- data.frame(year = seq(min(terrorism$year), max(terrorism$year),
length.out = 51))
# creating prediction model
pred <- predict(mod, newdata = pred.df, se.fit = TRUE)

# fitting exp count
pred.df2$count <- exp(pred$fit)
# generating lowest count value for ribbon (CI)
pred.df2$countmin <- exp(pred$fit - 2 * pred$se.fit)
# generating highest count value for ribbon (CI)
pred.df2$countmax <- exp(pred$fit + 2 * pred$se.fit)
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
colors <- c("Predicted" = "red", "Expected" = "blue")
ggplot(terrorism,aes(x=year,y=count)) +
scale_x_continuous(limits=c(1970,2022),breaks=c(1970,
1975,1980,1985,1990,1995,
2000,2005,2010,2015,2020)) +
geom_point() +
geom_ribbon(data = pred.df2, aes(ymin = countmin, ymax = countmax), alpha =
0.3) +
geom_line(data = pred.df2, aes(y = count, color="Predicted")) +
# Add vertical lines
geom_vline(xintercept = c(1970,1980,1990,2000,2010,2020),
linetype="dotted") +
# Add growth rate per decade
geom_segment(aes(x = 1970, y = 750, xend = 1980, yend = 750))+
geom_text(aes(1975,
y = 750,
label = "21.78 %"),
color = 'blue',
size = 4,
nudge_y = 120) +
geom_segment(aes(x = 1980, y = 1500, xend = 1990, yend = 1500))+
geom_text(aes(1985,
y = 1500,
label = "10.93 %"),
color = 'blue',
size = 4,
nudge_y = 120) +
geom_segment(aes(x = 1990, y = 2500, xend = 2000, yend = 2500))+
geom_text(aes(1995,
y = 2500,

label = "10.75 %"),
color = 'blue',
size = 4,
nudge_y = 120) +
geom_segment(aes(x = 2000, y = 3250, xend = 2010, yend = 3250))+
geom_text(aes(2005,
y = 3250,
label = "10.58 %"),
color = 'blue',
size = 4,
nudge_y = 120) +
geom_segment(aes(x = 2010, y = 4000, xend = 2020, yend = 4000))+
geom_text(aes(2015,
y = 4000,
label = "0.02 %"),
color = 'blue',
size = 4,
nudge_y = 120) +
annotate(geom = 'label', label = paste0("Overall Predicted Growth Rate: ",
round(pred_rate, digits = 2), "%"),
x = -Inf, y = Inf, hjust = 0, vjust = 1) +
labs(x = "Year",
y = "Count",
color = "Legend") +
ggtitle("Terrorism") +
scale_color_manual(values = colors)
# Diversity and Inclusion
# Not enough values until 2000
diversity <- subset(byterm, byterm$term == "Diversity and inclusion")
d4 = data.frame(subset(diversity, diversity$year >=2000 & diversity$year
<=2010))
d5 = data.frame(subset(diversity, diversity$year >=2010 & diversity$year
<=2020))
yr_list = list(d4,d5,diversity)
yr_tmp = list()
for (i in 1:3){
dt = yr_list[[i]]
# fitting model based on reference code
mod <- glm(count~year, data = dt, family = "poisson")
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
yr_tmp[[i]] <- pred_rate
}

#Convert list to dataframe
yr_df <- data.frame(yr_tmp)
#Add correct column name per decade
names(yr_df) <- c("2000-2010","2010-2020","1970-2020")
#Round numbers to 2 digits and add %
yr_df <- round(yr_df, 2)
yr_df[] <- Map(paste, yr_df, "%")
yr_df
## 2000-2010 2010-2020 1970-2020
## 1 27.86 % 30.12 % 29.24 %
# Subset term
diversity <- subset(byterm, byterm$term == 'Diversity and inclusion')
# fitting model based on reference code
mod <- glm(count~year, data = diversity, family = "poisson")
# length.out measures length of x-axis which is 51 (1970-2020)
pred.df2 <- data.frame(year = seq(min(diversity$year), max(diversity$year),
length.out = 51))
# creating prediction model
pred <- predict(mod, newdata = pred.df, se.fit = TRUE)
# fitting exp count
pred.df2$count <- exp(pred$fit)
# generating lowest count value for ribbon (CI)
pred.df2$countmin <- exp(pred$fit - 2 * pred$se.fit)
# generating highest count value for ribbon (CI)
pred.df2$countmax <- exp(pred$fit + 2 * pred$se.fit)
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
colors <- c("Predicted" = "red", "Expected" = "blue")
ggplot(diversity,aes(x=year,y=count)) +
scale_x_continuous(limits=c(1970,2022),breaks=c(1970,
1975,1980,1985,1990,1995,
2000,2005,2010,2015,2020)) +
geom_point() +
48
geom_ribbon(data = pred.df2, aes(ymin = countmin, ymax = countmax), alpha =
0.3) +
geom_line(data = pred.df2, aes(y = count, color="Predicted")) +
# Add vertical lines
geom_vline(xintercept = c(1970,1980,1990,2000,2010,2020),
linetype="dotted") +
geom_segment(aes(x = 1970, y = 100, xend = 1980, yend = 100))+
# Add growth rate per decade
geom_text(aes(1975,
y = 100,
label = "N/A"),
color = 'blue',
size = 4,
nudge_y = 12) +
geom_segment(aes(x = 1980, y = 200, xend = 1990, yend = 200))+
geom_text(aes(1985,
y = 200,
label = "N/A"),
color = 'blue',
size = 4,
nudge_y = 12) +
geom_segment(aes(x = 1990, y = 300, xend = 2000, yend = 300))+
geom_text(aes(1995,
y = 300,
label = "N/A"),
color = 'blue',
size = 4,
nudge_y = 12) +
geom_segment(aes(x = 2000, y = 400, xend = 2010, yend = 400))+
geom_text(aes(2005,
y = 400,
label = "27.86 %"),
color = 'blue',
size = 4,
nudge_y = 12) +
geom_segment(aes(x = 2010, y = 500, xend = 2020, yend = 500))+
geom_text(aes(2015,
y = 500,
label = "30.12 %"),
color = 'blue',
size = 4,
nudge_y = 12) +
annotate(geom = 'label', label = paste0("Overall Predicted Growth Rate: ",
49
round(pred_rate, digits = 2), "%"),
x = -Inf, y = Inf, hjust = 0, vjust = 1) +
ggtitle("Diversity and Inclusion") +
labs(x = "Year",
y = "Count",
color = "Legend") +
scale_color_manual(values = colors)
# Racism
racism <- subset(byterm, byterm$term == "Racism")
d1 = data.frame(subset(racism, racism$year <=1980))
d2 = data.frame(subset(racism, racism$year >=1980 & racism$year <=1990))
d3 = data.frame(subset(racism, racism$year >=1990 & racism$year <=2000))
d4 = data.frame(subset(racism, racism$year >=2000 & racism$year <=2010))
d5 = data.frame(subset(racism, racism$year >=2010 & racism$year <=2020))
yr_list = list(d1,d2,d3,d4,d5, racism)
yr_tmp = list()
for (i in 1:6){
dt = yr_list[[i]]
# fitting model based on reference code
mod <- glm(count~year, data = dt, family = "poisson")
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
yr_tmp[[i]] <- pred_rate
}
#Convert list to dataframe
yr_df <- data.frame(yr_tmp)
#Add correct column name per decade
names(yr_df) <-
c("1970-1980","1980-1990","1990-2000","2000-2010","2010-2020","1970-2020")
#Round numbers to 2 digits and add %
yr_df <- round(yr_df, 2)
yr_df[] <- Map(paste, yr_df, "%")
yr_df
## 1970-1980 1980-1990 1990-2000 2000-2010 2010-2020 1970-2020
## 1 1.61 % 11.76 % 11.72 % 7.07 % 8.29 % 8.76 %
# Subset term
racism <- subset(byterm, byterm$term == 'Racism')
# fitting model based on reference code
mod <- glm(count~year, data = racism, family = "poisson")
50
# length.out measures length of x-axis which is 51 (1970-2020)
pred.df2 <- data.frame(year = seq(min(racism$year), max(racism$year),
length.out = 51))
# creating prediction model
pred <- predict(mod, newdata = pred.df, se.fit = TRUE)
# fitting exp count
pred.df2$count <- exp(pred$fit)
# generating lowest count value for ribbon (CI)
pred.df2$countmin <- exp(pred$fit - 2 * pred$se.fit)
# generating highest count value for ribbon (CI)
pred.df2$countmax <- exp(pred$fit + 2 * pred$se.fit)
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
colors <- c("Predicted" = "red", "Expected" = "blue")
ggplot(racism,aes(x=year,y=count)) +
scale_x_continuous(limits=c(1970,2022),breaks=c(1970,
1975,1980,1985,1990,1995,
2000,2005,2010,2015,2020)) +
geom_point() +
geom_ribbon(data = pred.df2, aes(ymin = countmin, ymax = countmax), alpha =
0.3) +
geom_line(data = pred.df2, aes(y = count, color="Predicted")) +
# Add vertical lines
geom_vline(xintercept = c(1970,1980,1990,2000,2010,2020),
linetype="dotted") +
# Add growth rate per decade
geom_segment(aes(x = 1970, y = 500, xend = 1980, yend = 500))+
geom_text(aes(1975,
y = 500,
label = "1.61 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 1980, y = 1250, xend = 1990, yend = 1250))+
geom_text(aes(1985,
y = 1250,
51
label = "11.76 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 1990, y = 2000, xend = 2000, yend = 2000))+
geom_text(aes(1995,
y = 2000,
label = "11.72 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 2000, y = 2750, xend = 2010, yend = 2750))+
geom_text(aes(2005,
y = 2750,
label = "7.07 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 2010, y = 3500, xend = 2020, yend = 3500))+
geom_text(aes(2015,
y = 3500,
label = "8.29 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
annotate(geom = 'label', label = paste0("Overall Predicted Growth Rate: ",
round(pred_rate, digits = 2), "%"),
x = -Inf, y = Inf, hjust = 0, vjust = 1) +
ggtitle("Racism") +
labs(x = "Year",
y = "Count",
color = "Legend") +
scale_color_manual(values = colors)
# Liberalism
liberalism <- subset(byterm, byterm$term == "Liberalism")
d1 = data.frame(subset(liberalism, liberalism$year <=1980))
d2 = data.frame(subset(liberalism, liberalism$year >=1980 & liberalism$year
<=1990))
d3 = data.frame(subset(liberalism, liberalism$year >=1990 & liberalism$year
<=2000))
d4 = data.frame(subset(liberalism, liberalism$year >=2000 & liberalism$year
<=2010))
d5 = data.frame(subset(liberalism, liberalism$year >=2010 & liberalism$year
52
<=2020))
yr_list = list(d1,d2,d3,d4,d5,liberalism)
yr_tmp = list()
for (i in 1:6){
dt = yr_list[[i]]
# fitting model based on reference code
mod <- glm(count~year, data = dt, family = "poisson")
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
yr_tmp[[i]] <- pred_rate
}
#Convert list to dataframe
yr_df <- data.frame(yr_tmp)
#Add correct column name per decade
names(yr_df) <-
c("1970-1980","1980-1990","1990-2000","2000-2010","2010-2020","1970-2020")
#Round numbers to 2 digits and add %
yr_df <- round(yr_df, 2)
yr_df[] <- Map(paste, yr_df, "%")
yr_df
## 1970-1980 1980-1990 1990-2000 2000-2010 2010-2020 1970-2020
## 1 3.95 % 8.73 % 10.29 % 6.28 % -1.89 % 7.25 %
# Subset term
liberalism <- subset(byterm, byterm$term == 'Liberalism')
# fitting model based on reference code
mod <- glm(count~year, data = liberalism, family = "poisson")
# length.out measures length of x-axis which is 51 (1970-2020)
pred.df2 <- data.frame(year = seq(min(liberalism$year), max(liberalism$year),
length.out = 51))
# creating prediction model
pred <- predict(mod, newdata = pred.df, se.fit = TRUE)
# fitting exp count
pred.df2$count <- exp(pred$fit)
# generating lowest count value for ribbon (CI)
pred.df2$countmin <- exp(pred$fit - 2 * pred$se.fit)
# generating highest count value for ribbon (CI)
53
pred.df2$countmax <- exp(pred$fit + 2 * pred$se.fit)
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
colors <- c("Predicted" = "red", "Expected" = "blue")
ggplot(liberalism,aes(x=year,y=count)) +
scale_x_continuous(limits=c(1970,2022),breaks=c(1970,
1975,1980,1985,1990,1995,
2000,2005,2010,2015,2020)) +
geom_point() +
geom_ribbon(data = pred.df2, aes(ymin = countmin, ymax = countmax), alpha =
0.3) +
geom_line(data = pred.df2, aes(y = count, color="Predicted")) +
# Add vertical lines
geom_vline(xintercept = c(1970,1980,1990,2000,2010,2020),
linetype="dotted") +
# Add growth rate per decade
geom_segment(aes(x = 1970, y = 500, xend = 1980, yend = 500))+
geom_text(aes(1975,
y = 500,
label = "3.95 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 1980, y = 1250, xend = 1990, yend = 1250))+
geom_text(aes(1985,
y = 1250,
label = "8.73 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 1990, y = 2000, xend = 2000, yend = 2000))+
geom_text(aes(1995,
y = 2000,
label = "10.29 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 2000, y = 2750, xend = 2010, yend = 2750))+
geom_text(aes(2005,
y = 2750,
54
label = "6.28 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
geom_segment(aes(x = 2010, y = 3500, xend = 2020, yend = 3500))+
geom_text(aes(2015,
y = 3500,
label = "-1.89 %"),
color = 'blue',
size = 4,
nudge_y = 150) +
annotate(geom = 'label', label = paste0("Overall Predicted Growth Rate: ",
round(pred_rate, digits = 2), "%"),
x = -Inf, y = Inf, hjust = 0, vjust = 1) +
ggtitle("Liberalism") +
labs(x = "Year",
y = "Count",
color = "Legend") +
scale_color_manual(values = colors)
# Conservative
conservative <- subset(byterm, byterm$term == "Conservative")
d1 = data.frame(subset(conservative, conservative$year <=1980))
d2 = data.frame(subset(conservative, conservative$year >=1980 &
conservative$year <=1990))
d3 = data.frame(subset(conservative, conservative$year >=1990 &
conservative$year <=2000))
d4 = data.frame(subset(conservative, conservative$year >=2000 &
conservative$year <=2010))
d5 = data.frame(subset(conservative, conservative$year >=2010 &
conservative$year <=2020))
yr_list = list(d1,d2,d3,d4,d5, conservative)
yr_tmp = list()
for (i in 1:6){
dt = yr_list[[i]]
# fitting model based on reference code
mod <- glm(count~year, data = dt, family = "poisson")
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
yr_tmp[[i]] <- pred_rate
}
#Convert list to dataframe
yr_df <- data.frame(yr_tmp)
#Add correct column name per decade
55
names(yr_df) <-
c("1970-1980","1980-1990","1990-2000","2000-2010","2010-2020","1970-2020")
#Round numbers to 2 digits and add %
yr_df <- round(yr_df, 2)
yr_df[] <- Map(paste, yr_df, "%")
yr_df
## 1970-1980 1980-1990 1990-2000 2000-2010 2010-2020 1970-2020
## 1 11.27 % 9.23 % 4.54 % 7.44 % -0.56 % 4.99 %
# Subset term
conservative <- subset(byterm, byterm$term == 'Conservative')
# fitting model based on reference code
mod <- glm(count~year, data = conservative, family = "poisson")
# length.out measures length of x-axis which is 51 (1970-2020)
pred.df2 <- data.frame(year = seq(min(conservative$year),
max(conservative$year), length.out = 51))
# creating prediction model
pred <- predict(mod, newdata = pred.df, se.fit = TRUE)
# fitting exp count
pred.df2$count <- exp(pred$fit)
# generating lowest count value for ribbon (CI)
pred.df2$countmin <- exp(pred$fit - 2 * pred$se.fit)
# generating highest count value for ribbon (CI)
pred.df2$countmax <- exp(pred$fit + 2 * pred$se.fit)
# calculate the percentage growth rate
pred_rate <- (exp(summary(mod)$coefficients[2,1]) - 1) * 100
colors <- c("Predicted" = "red", "Expected" = "blue")
ggplot(conservative,aes(x=year,y=count)) +
scale_x_continuous(limits=c(1970,2022),breaks=c(1970,
1975,1980,1985,1990,1995,
2000,2005,2010,2015,2020)) +
geom_point() +
geom_ribbon(data = pred.df2, aes(ymin = countmin, ymax = countmax), alpha =
0.3) +
56
geom_line(data = pred.df2, aes(y = count, color="Predicted")) +
# Add vertical lines
geom_vline(xintercept = c(1970,1980,1990,2000,2010,2020),
linetype="dotted") +
# Add growth rate per decade
geom_segment(aes(x = 1970, y = 2500, xend = 1980, yend = 2500))+
geom_text(aes(1975,
y = 2500,
label = "11.27 %"),
color = 'blue',
size = 4,
nudge_y = 300) +
geom_segment(aes(x = 1980, y = 3550, xend = 1990, yend = 3550))+
geom_text(aes(1985,
y = 3550,
label = "9.23 %"),
color = 'blue',
size = 4,
nudge_y = 300) +
geom_segment(aes(x = 1990, y = 5000, xend = 2000, yend = 5000))+
geom_text(aes(1995,
y = 5000,
label = "4.54 %"),
color = 'blue',
size = 4,
nudge_y = 300) +
geom_segment(aes(x = 2000, y = 6250, xend = 2010, yend = 6250))+
geom_text(aes(2005,
y = 6250,
label = "7.44 %"),
color = 'blue',
size = 4,
nudge_y = 300) +
geom_segment(aes(x = 2010, y = 7500, xend = 2020, yend = 7500))+
geom_text(aes(2015,
y = 7500,
label = "-0.56 %"),
color = 'blue',
size = 4,
nudge_y = 300) +
annotate(geom = 'label', label = paste0("Overall Predicted Growth Rate: ",
round(pred_rate, digits = 2), "%"),
x = -Inf, y = Inf, hjust = 0, vjust = 1) +
57
ggtitle("Conservative") +
labs(x = "Year",
y = "Count",
color = "Legend") +
scale_color_manual(values = colors)
```











